

\noindent\begin{tabularx}{\textwidth}{lX}
\textbf{Thesis} & Application of State of the Art Deep Reinforcement Learning Algorithms To The Cryptocurrency Trading Problem.\\
\textbf{Student} & Mr. Daniel Ekwuazi\\
\textbf{Student ID.} & 61610024 \\
\textbf{Degree} & Master of Engineering \\
\textbf{Program} & Computational Intelligence Systems \\
\textbf{year.} & 2021 \\
\textbf{Thesis Advisor \indent\indent} & Asst. Prof. Dr. Chaiwat Nuthong \\
\end{tabularx}

\begin{center}
\section*{\LARGE Abstract}

The cryptocurrency market has been known to be volatile, which presents an opportunity to profit from swings. Although buy and hold (\texttt{HODL}) has shown to be the best performing strategy in the long term, yielding an outstanding ROI, there are efforts to automate the trading process. The most traditional approach is using statistical indicators to signal trading actions, sometimes assisted by a simple machine learning (ML) as a price predictor. Another new-age approach that is the topic of interest of this research is trading using reinforcement learning (RL). RL is an application of ML which incorporates learning process by exploring states and searching the best action based on the states. A good action is granted a positive reward, vice-versa. In this research, multiple RL algorithms in continuous and discrete action spaces are used to perform backtrading in the Bitcoin spot market. Trained on a hour-level crab market, the models' performance are tested in bull, crab, and bear markets in hour and minute levels.

(results later)

This research contributes as the primary research in comparing different RL algorithms' performance in trading environment based on algorithm and action space types.

\textbf{Keywords:} portfolio management, automated trading, machine learning, genetic algorithms, reinforcement learning.

\end{center}


