\begin{thebibliography}{1}

% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.



\bibitem{bib:backpain}
C. Gent, J. Dols, C. Rover, R. Sing and H. Vet, "Heavy Bags Lead to Back Pain in Children", Medscape, 2003. [Online]. Available: http://www.medscape.com/viewarticle/455563\_4. [Accessed: 04- May- 2016].

\bibitem{bib:What is NFC}
  "What Is NFC? - NFC Forum", NFC Forum, 2016. [Online]. Available: http://nfc-forum.org/what-is-nfc/. [Accessed: 04-May-2016].

\bibitem{bib:NFC_bootstrapping}
"NFC Forum: NFC as Technology Enabler", NFC Forum. [Online]. Available: http://members.nfc-forum.org/aboutnfc/tech\_enabler/. [Accessed: 18- May- 2016].

\bibitem{bib:NFC Phones List}
"List of NFC phones", NFC World+, 2016. [Online]. Available: http://www.nfcworld.com/nfc-phones-list/. [Accessed: 04-May- 2016].

\bibitem{bib:Chromecast}
  "Chromecast - Google", Google.com, 2016. [Online]. Available: https://www.google.com/chromecast. [Accessed: 04-May-2016].
  
\bibitem{bib:UPnP Device Architecture}
  UPnP Forum, "UPnP™ Device Architecture 1.1", 2008. 
  
\bibitem{bib:FSPL}
J. Yang and Y. Chen, "Indoor Localization Using Improved RSS-Based Lateration Methods," Global Telecommunications Conference, 2009. GLOBECOM 2009. IEEE, Honolulu, HI, 2009, pp. 1-6.

\bibitem{bib:ARP}
D. Plummer, "RFC 826 - Ethernet Address Resolution Protocol: Or Converting Network Protocol Addresses to 48.bit Ethernet Address for Transmission on Ethernet Hardware", 1982. [Online]. Available: https://tools.ietf.org/html/rfc826. [Accessed: 18- May- 2016].

\bibitem{bib:ARP Timeout}
"arp(7): ARP kernel module - Linux man page", Linux.die.net. [Online]. Available: http://linux.die.net/man/7/arp. [Accessed: 04-May-2016].

\bibitem{bib:bluetooth_vs_wifi}
Mautz, R., 2012. Indoor positioning technologies (Doctoral dissertation, Habilitationsschrift ETH Zürich, 2012).

\bibitem{bib:distance_with_RSSI}
J. Rogowski, "Distance measurement using radio frequency identification technology," Scientific and Technical Conference "Computer Sciences and Information Technologies" (CSIT), 2015 Xth International, Lviv, 2015, pp. 9-15.
doi: 10.1109/STC-CSIT.2015.7325420
keywords: {radiofrequency identification;asset localisation applicable format;competitive product;distance measurement;radio frequency identification technology;real-time localisation system;Accuracy;Algorithm design and analysis;Antennas;Calibration;Radiofrequency identification;Real-time systems;Receivers;RFID;asset localisation system},
URL: http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=\&arnumber=7325420\&isnumber=7325415

\bibitem{bib:rssi_reliability}
Qian Dong and W. Dargie, "Evaluation of the reliability of RSSI for indoor localization," Wireless Communications in Unusual and Confined Areas (ICWCUCA), 2012 International Conference on, Clermont Ferrand, 2012, pp. 1-6.
doi: 10.1109/ICWCUCA.2012.6402492
URL: http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=\&arnumber=6402492\&isnumber=6402322

\bibitem{bib:timeofflight}
L. Schauer, F. Dorfmeister and M. Maier, "Potentials and limitations of WIFI-positioning using Time-of-Flight," Indoor Positioning and Indoor Navigation (IPIN), 2013 International Conference on, Montbeliard-Belfort, 2013, pp. 1-9.
doi: 10.1109/IPIN.2013.6817861
URL: http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=\&arnumber=6817861\&isnumber=6817839

\bibitem{bib:Chronos}
D.  Vasisht, S.  Kumar and D.  Katabi, "Decimeter-Level Localization with a Single WiFi Access Point", in 13th USENIX Symposium on Networked Systems Design and Implementation (NSDI 16), 2016, pp. 165-178.

\end{thebibliography}