\chapter{Introduction}
\label{Introduction}

\section{Background}
Cryptocurrency markets is often associated with price volatility. Its market cap has increased tremendously over the years to almost USD 3 trillion in late 2021\footnote{https://www.tradingview.com/symbols/CRYPTOCAP-TOTAL/}. Average investors are at risk of the fear of missing out (FOMO) and therefore prone to making investment decisions detrimental to their finances. When it comes to cryptocurrency, the market's popular action sentiment is to buy and hold. This has proven to be the best strategy in the long term, generating an astronomical return-of-investment (ROI), as can be seen with Bitcoin's return in 10 years\footnote{https://www.tradingview.com/chart/?symbol=BTCUSD}. Such tremendous return-of-investment ROI is exciting, but the buy and hold sentiment encourages that one perpetually holds yet without exit strategy; this makes investment returns to be suboptimal. Therefore, there is a need to equip a strategy-building framework to maximize returns, preferably with the assistance of automation.

Besides statistics and basic machine learning (ML) approaches, many switch to explore the field of Reinforcement Learning (RL) for trading automation: a ML branch which learns from rewards and punishments over exploring actions. Reinforcement Learning algorithms have achieved outstanding performances in various domains in recent history, with agents such as Alpha GO, Alpha Zero beating a human at the complex game of Go and Chess respectively. State of the art performance has also been achieved in Atari gameplays using Deep Q-Network (DQN) and in robotics. Various DL algorithms have also been applied to stock and cryptocurrency trading bots.

\section{Problem Description}

Deciding when to buy, sell or hold, for investors who would like to take advantage of the cryptocurrency market swings and make gains in the short term, can be very challenging. Due to the high volatility and nonstationarity of cryptocurrency markets, sometimes traditional ML approaches do not perform as efficiently as wished. RL improves ML by being able to take actions based on real-time states and previous feedbacks, in automation. Since there are a vast selection of RL algorithms to choose from, therefore, it is necessary to examine each algorithm's advantages and disadvantages by comparing their performances against another.

\section{Research Objectives}
This research aims to evaluate and compare several RL algorithms and action spaces (DQN, PPO, SAC, A2C, and A3C) and traditional trading algorithms (HODL, MACD) in performing a Bitcoin trading (sell, buy, hold). The comparison is based on the following key metrics: ROI, MDD, computational resources used, training duration, and inference. On top of that, this research compares between continuous action space vs discrete action space for the problem setting.

% Discrete = buy all, sell all, hold all; continuous: trade some
% Add list of jargons/terms in appendix??

\section{Research Scope}
The scope of this research is as follows:
\begin{itemize}
	\item Trading decisions are done and calculated through backtesting.
	\item Trading data consists of training and testing data, comes from only one trading pair, which is \texttt{BTCUSD}:
	\begin{itemize}
		\item Training data: 11,144 data points of a crab market in a hour-level timeframe.
		\item Testing data: 2,000 data points in minute and hour levels, both in bull/crab and bear trends.
	\end{itemize}
	\item The actions are limited to buying, holding, and selling Bitcoin in the spot market.
	\item The performance are measured using the following metrics: portfolio return, maximum drawdown (MDD), and Sortino Ratio.
\end{itemize}

\section{Contributions}
This research serves as one of the first to compare the performance of different RL algorithms in the application of cryptocurrency trading, according to the type of the algorithm (policy-based, value-based, and combined) and the type of action space (discrete, continuous). From the results, this work will summarize the advantages and disadvantages of each algorithm in the application of trading in the spot market, and suggest future researchers on how to pick models based on specific cases.